Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-05 prop.tex
prop.tex \section{Conclusion and Discussion} Keep editing according to "The Craft of Research"...
prop.tex \section{Conclusion and Discussion} Updating...

\documentclass{article}
\usepackage[ backend=biber]{biblatex}
\addbibresource{proposal/prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}

@@

\begin{thm}[Shapley~\cite{Shapley1971}]\label{thm:Shapley}
  Every (classical) convex interval-valued probability measure has a
  non-empty core.
\end{thm}

@@

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. This raises an important philosophical question with
immense practical relevance in the context of quantum computing. The
question, which we could largely bypass in the classical case, is
whether there is, in the background of all the measurements and probabilities,
a ``real'' infinitely-precise quantum state that is being approximated
and that, in principle, can be more and more accurately described
given more and more resources. In particular, we could summarize our
examples and Gleason's theorem in table~\ref{table_long}. 
\begin{table}[ht]
\center{%
\begin{tabular}{c|cccc}
Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
\hline 
Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
\hline 
$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $1/2$ & \ldots{} & $0$\tabularnewline
\hline 
Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
\hline 
Count of states might correspond to $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
\hline 
How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
\end{tabular}}\caption{Summarize example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value}
and Gleason's theorem}
\label{table_long}
\end{table}
Although the tend is clear, we still need more examples to fill the
blank and to prove our idea. Some research questions might be
\begin{description}
\item [{Research Question.}] Confirm that there is always an interval-valued
probability measure with an empty-core if the length of the interval
is bigger than zero. 
\item [{Research Question.}] In example~\ref{ex:three-dimensional-three-value}
and \ref{ex:three-dimensional-4-value}, we pick a possible candidate
corresponding to an interval-valued probability measure by only considering
the state whose interval-valued probability is $\necess$. Define
a general method which could be used to determine whether an interval-valued
probability measure is closer to the Born rule or not. 
\item [{Research Question.}] Confirm that as the number and precision
of the intervals increase the quantum interval-valued probability
measure converges to the measure induced by the Born rule. 
\end{description}
Since the validity of Gleason's theorem in a world with finite-precision
measurements is a question, the natural follow-up questions is to
investigate the status of the theorems of Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker for quantum interval-valued probability measures
as well. Going further we actually have to concede not just the infinite
accuracy of the quantum state, but its very existence as a ``real''
entity that exists independently of measurements and probabilities.
The reasons for this second radical position are as follows. First
arguments embedded in the proof of the Kochen-Specker theorem essentially
rule out the existence of a sample space as the probabilities of events
cannot be consistently expressed using core assignments to elements
of the sample space. Second, the frequency interpretation of probability
which is already problematic in the classical case, becomes untenable
in the quantum case. In both cases, but much more in the quantum case,
it is much more sensible to interpret probability in the Bayesian
sense as ``lack of knowledge''. This, and similar arguments elegantly
expressed by recent work on Quantum Bayesianism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
suggest that the quantum state is more like an interactive system
in computer science parlance. In other words, the state is only determined
by its interactions with the environment or observers. A rough but
useful analogy in the context of computer science would be a web server:
the state of such a system cannot be said to exist independently of
the interactions with clients; each interaction with a client determines
a future state of the system and may affect future interactions. Crucially,
each client may have a \emph{different} view of the web server that
is consistent with their own history of interactions. This computational
perspective agrees with the philosophical position of QBism~\cite{VonBaeyer2016}
that asserts that the quantum state is subjective: each observer has
a different view of the quantum system that is consistent with their
previous observations and that allows that observer, independently
of other observers, to assign beliefs (i.e., probabilities) to possible
future interactions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\printbibliography
\end{document}

>>>>

\documentclass{article}
\usepackage[ backend=biber]{biblatex}
\addbibresource{proposal/prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}

@@

\begin{thm}[Shapley~\cite{Shapley1971,,Grabisch2016}]\label{thm:Shapley}
  Every (classical) convex interval-valued probability measure has a
  non-empty core.
\end{thm}

@@

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. This raises an important philosophical question with
immense practical relevance in the context of quantum computing. The
question, which we could largely bypass in the classical case, is
whether there is, in the background of all the measurements and probabilities,
a ``real'' infinitely-precise quantum state that is being approximated
and that, in principle, can be more and more accurately described
given more and more resources. Although a coarse quantum interval-valued
probability measure may not be induced by one infinitely-precise quantum
state, it might be induced by many quantum states when we examine
different part of its probability assignment. Our examples and Gleason's
theorem suggests that when we increase the measurement resources,
interval-valued probability measures could more and more likely be
identified to a particular state as shown in table~\ref{table_long}.
\begin{table}[ht]
\center{%
\begin{tabular}{c|cccc}
Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
\hline 
Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $\frac{1}{2}$ & \ldots{} & $0$\tabularnewline
Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
Count of states might correspond to $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
\hline 
How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
\end{tabular}}\caption{Relation between measurement resources and interval-valued probability
measures}
\label{table_long}
\end{table}
Additional work is in progress on the following research questions:
\begin{description}
\item [{Research Question.}] Confirm that there is always an interval-valued
probability measure with an empty-core if the length of the interval
is bigger than zero. 
\item [{Research Question.}] In example~\ref{ex:three-dimensional-three-value}
and \ref{ex:three-dimensional-4-value}, we pick a possible candidate
corresponding to an interval-valued probability measure by only considering
the state whose interval-valued probability is $\necess$. Find a
general method which could be used to determine whether an interval-valued
probability measure is closer to the Born rule or not. 
\item [{Research Question.}] Confirm that as the number and precision
of the intervals increase the quantum interval-valued probability
measure converges to the measure induced by the Born rule. 
\item [{Research Question.}] Investigate the status of the theorems of
Gleason, Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker for quantum interval-valued probability measures.
\end{description}
Although we tried to induce a quantum interval-valued probability
measure from a real quantum state, our investigation leaves an open
question of whether there exists a ``real'' entity that exists independently
of measurements and probabilities. This idea is consistent with the
elegantly recent work on Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
which suggests that the quantum state is more like an interactive
system in computer science parlance. Moreover, the quantum state is
subjective: each observer has a different view of the quantum system
that is consistent with their previous observations and that allows
that observer, independently of other observers, to assign beliefs
(i.e., probabilities) to possible future interactions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{}%
\begin{comment}
 \bibliographystyle{plain}
\bibliography{proposal/prop}

\end{comment}
\printbibliography 
\end{document}
